Replication Survey

### 2023-09-28 docs/manuscript/manuscript.tex
Update author info

%%%%%%%%%%%%%%%%%%%%
\newpage
\noindent PETER KEDRON is an Associate Professor in the School of Geographical Science and Urban Planning and core faculty member in the Spatial Analysis Research Center (SPARC) at Arizona State University, Tempe, AZ, 85283, US. Email: Peter.Kedron@asu.edu. His research interests include spatial analysis, geographic information science, economic geography, and the accumulation of knowledge about geographic phenomena. \\

\noindent JOSEPH HOLLER is an Assistant Professor of Geography at Middlebury College, Middlebury, VT, 05753, US. Email: \\

\noindent SARAH BARDIN is a PhD candidate ...

>>>>

%%%%%%%%%%%%%%%%%%%%
\newpage
\noindent PETER KEDRON is an Associate Professor in Department of Geography at University of California Santa Barbara, Santa Barbara CA, 93106, US. Email: peterkedron@ucsb.edu. His research program develops and uses spatial analytical methods to understanding persistently uneven patterns of spatial development. His recent work focuses on improving the production and accumulation of knowledge used to benefit society through policy. \\

\noindent JOSEPH HOLLER is an Assistant Professor of Geography at Middlebury College. He is human geographer and geographic information scientist with research interests in social vulnerability and adaptation in the context of climate change and environmental degradation. His research intersects with work in political ecology, development geography, human dimensions of global change, and geographic information science. \\

\noindent SARAH BARDIN is a doctoral student in Geography at the School of Geographical Sciences and Urban Planning at Arizona State University. Her research focuses on leveraging spatial modeling and GIS to generate policy-relevant, actionable insights from data.
